---
title: "03 Automated Machine Learning with H20"
date: "2021-06-05"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

```{r}
library(tidyverse)
library(readxl)
library(skimr)
library(GGally)

# Load Data data definitions
employee_attrition_tbl <- read_csv("HR-Employee-Attrition.csv")

# Create data tibble, to potentially debug the plot_ggpairs function (because it has a data argument)
data <- employee_attrition_tbl %>%
  select(Attrition, Age, Gender, MaritalStatus, NumCompaniesWorked, Over18, DistanceFromHome)

plot_ggpairs <- function(data, color = NULL, density_alpha = 0.5) {
  
  color_expr <- enquo(color)
  
  if (rlang::quo_is_null(color_expr)) {
    
    g <- data %>%
      ggpairs(lower = "blank") 
    
  } else {
    
    color_name <- quo_name(color_expr)
    
    g <- data %>%
      ggpairs(mapping = aes_string(color = color_name), 
              lower = "blank", legend = 1,
              diag = list(continuous = wrap("densityDiag", 
                                            alpha = density_alpha))) +
      theme(legend.position = "bottom")
  }
  
  return(g)
}


employee_attrition_tbl %>%
  select(Attrition, contains("income"), contains("rate"), contains("salary"), contains("stock")) %>%
  plot_ggpairs(Attrition)

```
####Answers from plottings

Q1. What can you deduce about the interaction between Monthly Income and Attrition?
c) Those that are leaving have a lower Monthly Income

Q2. What can you deduce about the interaction between Percent Salary Hike and Attrition? 
d) It’s difficult to deduce anything based on the visualization

Q3. What can you deduce about the interaction between Stock Option Level and Attrition?
b) Those that are staying have a higher stock option level

Q4. What can you deduce about the interaction between Environment Satisfaction and Attrition? 
c)It’s difficult to deduce anything based on the visualization

Q5. What can you deduce about the interaction between Work Life Balance and Attrition 
b) Those that are staying have a higher density of 2’s and 3’s

Q6. What Can you deduce about the interaction between Job Involvement and Attrition? 
d) It’s difficult to deduce anything based on the visualization

Q7. What can you deduce about the interaction between Over Time and Attrition?
b) The proportion of those staying that are working Over Time are high compared to those that are not staying

Q8. What can you deduce about the interaction between Training Times Last Year and Attrition? 
b) People that leave tend to have less annual trainings

Q9. What can you deduce about the interaction between Years At Company and Attrition?
b) People that leave tend to have less working years at the company

Q10. What can you deduce about the interaction between Years Since Last Promotion and Attrition? 
b) Those that are leaving have fewer years since last promotion than those that are staying


```{r}
library(h2o)
library(tidyverse)
library(readxl)
library(rsample)
library(recipes)

# Load the training & test dataset
products_backorders_tbl <- read_csv("product_backorders.csv")

products_backorders_tbl <- products_backorders_tbl  %>%
  mutate_if(is.character, as.factor)

set.seed(seed = 1113)

split_obj                       <- rsample::initial_split(products_backorders_tbl, prop = 0.85)
train_readable_tbl              <- training(split_obj)
test_readable_tbl               <- testing(split_obj)

# Specifiy the response and predictor variables
recipe_obj <- recipe(went_on_backorder ~., data = train_readable_tbl) %>% 
  step_zv(all_predictors()) %>% 
  prep()

train_tbl <- bake(recipe_obj, new_data = train_readable_tbl)
test_tbl  <- bake(recipe_obj, new_data = test_readable_tbl)

# Modeling
h2o.init()
# Split data into a training and a validation data frame
# Setting the seed is just for reproducability
split_h2o <- h2o.splitFrame(as.h2o(train_tbl), ratios = c(0.85), seed = 1234)
train_h2o <- split_h2o[[1]]
valid_h2o <- split_h2o[[2]]
test_h2o  <- as.h2o(test_tbl)
# run AutoML specifying the stopping criterion
# Set the target and predictors
y <- "went_on_backorder"
x <- setdiff(names(train_h2o), y)

automl_models_h2o <- h2o.automl(
  x = x,
  y = y,
  training_frame    = train_h2o,
  validation_frame  = valid_h2o,
  leaderboard_frame = test_h2o,
  max_runtime_secs  = 30,
  nfolds            = 5 
)

# View the leaderboard
automl_models_h2o@leaderboard

automl_models_h2o@leader

# Predicting using Leader Model
predictions <- h2o.predict(automl_models_h2o@leader, newdata = as.h2o(test_tbl))

predictions_tbl <- predictions %>% as_tibble()

predictions_tbl

# Save the leader model
automl_models_h2o@leader %>% h2o.saveModel(path = "h20_models/")



```

